---
title: "Conversion docx to Rmd"
author: "mattador Stackoverflow"
date: "30 10 2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Pandoc user guide: https://pandoc.org/MANUAL.html

Convert:   
- from doi to bibtex: https://doi2bib.org    
- from isbn to bibtex: http://doi-to-bibtex-converter.herokuapp.com; https://zbib.org/ ;  https://www.xarg.org/tools/isbn-to-bibtex/   
- from Word to markdown: https://word2md.com    

csl style:   
- look up the csl style of the selected journal   
- copy the csl style sheet   
- paste it into a new Rmd file and name it (e.g. linguistics.csl)   
- add the line "csl: linguistics.csl" to the yaml header of your Rmd article or book!

My adaptation: docx to html

```{r}
require(rmarkdown);require(devtools)
examplefile = "02d_Stellungsfelder_DEU_SLO.docx"
pandoc_convert(examplefile,to="markdown",output = "02d_Stellungsfelder_DEU_SLO.Rmd", options=c("--extract-media=."))
render("02d_Stellungsfelder_DEU_SLO.Rmd","html_document")
browseURL("02d_Stellungsfelder_DEU_SLO.html")
```

docx to latex:

```{r}
options(tinytex.verbose = TRUE)
require(rmarkdown);require(devtools)
examplefile = "02d_Stellungsfelder_DEU_SLO.docx"
pandoc_convert(examplefile,to="latex",output = "02d_Stellungsfelder_DEU_SLO.tex", options=c("--extract-media=."))
# render("02d_Stellungsfelder_DEU_SLO.tex","html_document")
# browseURL("02d_Stellungsfelder_DEU_SLO.html")

```


mattador Stackoverflow:

```{r}
require(rmarkdown);require(devtools)
examplefile=paste0(tempdir(),"/example.docx")
download.file("https://file-examples.com/wp-content/uploads/2017/02/file-sample_100kB.docx",destfile=examplefile)
pandoc_convert(examplefile,to="markdown",output = "example.rmd", options=c("--extract-media=."))

render(paste0(tempdir(), "/example.rmd"),"html_document")
browseURL(paste0(tempdir(),"/example.html"))
```

Zotero to bibtex:
[@Eisenberg_1994]

@book{Eisenberg_1994, place={Stuttgart Weimar}, edition={3., überarb. Aufl}, title={Grundriß der deutschen Grammatik}, ISBN={9783476012326}, publisher={Metzler}, author={Eisenberg, Peter}, year={1994} }


@book{3476012328,
    title = {Grundriss der deutschen Grammatik},
    author = {Peter Eisenberg},
    year = {1994},
    month = {11},
    day = {05},
    pagecount = {581},
    isbn = {9783476012326}
}
